---
title: '**Cyber Crimes in India**'
documentclass: report
date: "June 30, 2023."
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
    number_sections: yes
papersize: a4
fontsize: 11
geometry: margin=1in
mainfont: Times New Roman
---

# Cyber Crimes against Women and Children


## Introduction

In this section, the main interest is to carry out statistical analysis of the Cyber Crimes happening particularly against women and children.        
The major cyber crimes against women for which the data is collected by NCRB include: Cyber Blackmailing/Threatening, Cyber Bullying/Stalking, Cyber Pornography, Fake Profiles, Defamation/Morphing etc.        

## Cyber Crimes against Children

```{r, warning=FALSE, echo=FALSE, message=FALSE}
rm(list = ls())
library(readxl)
child21 = read_excel("2021 children.xlsx")
child20 = read_excel("2020 children.xlsx")
child19 = read_excel("2019 children.xlsx")
child18 = read_excel("2018 children.xlsx")
child17 = read_excel("2017 children.xlsx")
```

**Year 2020**

**State-Wise**

```{r, warning=FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
library(ggthemes)
ggplot(data = child20[1:28,], aes(x = state_ut, y = totalcrimes))+geom_bar(stat = "identity", fill = "#00c698")+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= totalcrimes ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crimes Against Children 2020: State Wise")+xlab("States")+ylab("Total Cyber Crimes aginst Children")
ggplot(data = child20[1:28,], aes(x = state_ut, y = totalcrimes))+geom_bar(stat = "identity", fill = "#0069c0")+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= totalcrimes ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crimes Against Children 2020: State Wise")+xlab("States")+ylab("Total Cyber Crimes aginst Children")
```

The states of Maharashtra, Uttar Pradesh, Karnataka, Kerala registered higher cyber-crimes against children in the year 2020.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = child20[1:28,], aes(x = state_ut, y = rate))+geom_bar(stat = "identity", fill = "#0b1d78")+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= rate ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crime Against Children Rates 2020: State Wise")+xlab("States")+ylab("Total Cyber Crimes per 1 lakh children population")
```
However, in terms of rates, Kerala has the maximum cyber crime rate against children in the year 2020

#### Runs Test for randomness

```{r, warning=FALSE, echo=FALSE, message=FALSE}
library(randtests)
runs.test(child20$rate[1:28] )
```

Since, p-value > 0.05, the results are coming out be non-significant. Thus, we conclude that the cyber-crime rates against children throughout the states is random.


#### Komlogorov-Smirnov Test

```{r, message=FALSE, echo=FALSE, warning=FALSE}
ks.test(child20$rate[1:28], child21$rate[1:28])
ks.test(child17$rate[-c(10, 30:39)], child21$rate[1:28])
ks.test(child18$rate[-c(10, 30:39)], child21$rate[1:28])
ks.test(child19$rate[-c(10, 30:39)], child21$rate[1:28])
ks.test(child19$rate[-c(10, 30:39)], child20$rate[1:28])
```
The distribution of cyber-crime rates against children is same for the years 2020 and 2021 throughout the states, however it differs significantly between the years 2021 amd 2017, 2018, 2019.

The distrubution of cases also differs significantly for the consecutive years 2019 and 2020 at 5% level of significance.

**U.T. Wise**

Data Visualization can be done for the Union Territories as follows: 

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = child20[30:37,], aes(x = state_ut, y = totalcrimes))+geom_bar(stat = "identity", fill = "#00a9b5", width = 0.5)+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= totalcrimes ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crimes Against Children 2020: U.T. Wise")+xlab("U.T.")+ylab("Total Cyber Crimes aginst Children")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = child20[30:37,], aes(x = state_ut, y = rate))+geom_bar(stat = "identity", fill = "#00c698", width = 0.5)+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= rate ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crime Against Children Rates 2020: U.T. Wise")+xlab("U.T.")+ylab("Total Cyber Crimes per 1 lakh children population")
```



**Year 2021**

**State-Wise**

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = child21[1:28,], aes(x = state_ut, y = totalcrimes))+geom_bar(stat = "identity", fill = "#0069c0")+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= totalcrimes ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crimes Against Children 2021: State Wise")+xlab("States")+ylab("Total Cyber Crimes aginst Children")

```

Maharashtra, Karnataka, Kerala, Assam and Uttar Pradesh have comparatively higher cyber crimes against children in 2021.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = child21[1:28,], aes(x = state_ut, y = rate))+geom_bar(stat = "identity", fill = "#0b1d78")+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= rate ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crime Against Children Rates 2021: State Wise")+xlab("States")+ylab("Total Cyber Crimes per 1 lakh children population")
```

However, in terms of rates, the state of Kerala again has the  maximum cyber crime rate against children.

**U.T. Wise**

Data for the Union Territories can also be viewed as folows:

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = child21[30:37,], aes(x = state_ut, y = totalcrimes))+geom_bar(stat = "identity", fill = "#00c698", width = 0.5)+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= totalcrimes ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crimes Against Children 2021: U.T. Wise")+xlab("U.T.")+ylab("Total Cyber Crimes aginst Children")

```
A huge increase in the cyber crimes against children can be noticed in Delhi as compared to previous year.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = child21[30:37,], aes(x = state_ut, y = rate))+geom_bar(stat = "identity", fill = "#0069c0", width = 0.5)+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= rate ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crime Against Children Rates 2021: U.T. Wise")+xlab("U.T.")+ylab("Total Cyber Crimes Rates children")
```



## Cyber Crimes against Women

```{r, warning=FALSE, echo=FALSE, message=FALSE}
rm(list = ls())
library(readxl)
women21 = read_excel("2021 women.xlsx")
women20 = read_excel("2020 women.xlsx")
women19 = read_excel("2019 women.xlsx")
women18 = read_excel("2018 women.xlsx")
women17 = read_excel("2017 women.xlsx")
```


#### Komlogorov-Smirnov Test

```{r, message=FALSE, echo=FALSE, warning=FALSE}
ks.test(women20$rate[1:28], women21$rate[1:28])
ks.test(women17$rate[-c(10, 30:39)], women21$rate[1:28])
ks.test(women18$rate[-c(10, 30:39)], women21$rate[1:28])
ks.test(women19$rate[-c(10, 30:39)], women21$rate[1:28])
ks.test(women19$rate[-c(10, 30:39)], women20$rate[1:28])
```

The distribution of cyber crime rates against women throughout the states is same for the years 2020 and 2021. However, the distribution differs significantly for the years 2017 and 2021.

**Year 2020**

**State-Wise**

```{r, warning=FALSE, echo=FALSE, message=FALSE}
library(ggplot2)
ggplot(data = women20[1:28,], aes(x = state_ut, y = totalcrimes))+geom_bar(stat = "identity", fill = "#0069c0")+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= totalcrimes ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crimes Against Women 2020: State Wise")+xlab("States")+ylab("Total Cyber Crimes aginst Women")
```

The states of Karnataka, Maharashtra, Assam have comparatively higher cyber crimes against women.


#### Runs Test for randomness

```{r, warning=FALSE, echo=FALSE, message=FALSE}
library(randtests)
runs.test(women20$rate[1:28] )
```


Since, p-value > 0.05, the results are coming out be non-significant. Thus, we conclude that the cyber-crime rates against women throughout the states is random.


```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = women20[1:28,], aes(x = state_ut, y = rate))+geom_bar(stat = "identity", fill = "#00c698")+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= rate ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crime Against Women Rates 2020: State Wise")+xlab("States")+ylab("Total Cyber Crimes per 1 lakh Women population")
```

In terms of rates, Karnataka has the maximum 8.73 cyber crimes against women followed by Assam and Telangana. 

**U.T. Wise**

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = women20[30:37,], aes(x = state_ut, y = totalcrimes))+geom_bar(stat = "identity", fill = "#0b1d78", width = 0.5)+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= totalcrimes ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crimes Against Women 2020: U.T. Wise")+xlab("U.T.")+ylab("Total Cyber Crimes aginst Women")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = women20[30:37,], aes(x = state_ut, y = rate))+geom_bar(stat = "identity", fill = "#00a9b5", width = 0.5)+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= rate ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crime Against Women Rates 2020: U.T. Wise")+xlab("U.T.")+ylab("Total Cyber Crime Rates Women")
```



**Year 2021**

**State-Wise**

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = women21[1:28,], aes(x = state_ut, y = totalcrimes))+geom_bar(stat = "identity", fill = "#00c698")+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= totalcrimes ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crimes Against Women 2021: State Wise")+xlab("States")+ylab("Total Cyber Crimes aginst Women")
```
Karnataka, Maharashtra and Assam are again the states with higher cyber crimes against women.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = women21[1:28,], aes(x = state_ut, y = rate))+geom_bar(stat = "identity", fill = "#0b1d78")+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= rate ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crime Against Women Rates 2021: State Wise")+xlab("States")+ylab("Total Cyber Crimes per 1 lakh Women population")
```

Again, the state of Karnataka has the maximum cyber crime rate against women followed by Assam, Telangana and Uttar Pradesh.

**U.T. Wise**

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = women21[30:37,], aes(x = state_ut, y = totalcrimes))+geom_bar(stat = "identity", fill = "#00a9b5", width = 0.5)+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= totalcrimes ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crimes Against Women 2021: U.T. Wise")+xlab("U.T.")+ylab("Total Cyber Crimes aginst Women")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
ggplot(data = women21[30:37,], aes(x = state_ut, y = rate))+geom_bar(stat = "identity", fill = "#00c698", width = 0.5)+theme_clean()+theme(axis.text.x = element_text(angle = 90, size = 8))+ geom_text(aes(label= rate ), vjust= -0.3, size=2.5)+ ggtitle("Cyber Crime Against Women Rates 2021: U.T. Wise")+xlab("U.T.")+ylab("Total Cyber Crime Rates Women")
```



\chapter*{Conclusion}


**References:**

* IAMAI and Kantar Joint Report (2023): 759 Million Indians Active Internet Users, to Reach 900 Million by 2025.       
* Crime in India Statistics (2021): National Crime Records Bureau (NCRB), Ministry of Home Affairs, Govt. of India, Volume II, Chapter 9, Table 9.A.1.        
* Crime in India Statistics (2016 - 2021): National Crime Records Bureau (NCRB), Ministry of Home Affairs, Govt. of India, Volume II, Chapter 9.                   
* Crime in India Statistics (2012 - 2015): National Crime Records Bureau (NCRB), Ministry of Home Affairs, Govt. of India, Chapter 18.                   
* Crime in India (2002 - 2011): National Crime Records Bureau (NCRB), Ministry of Home Affairs, Govt. of India, Chapter 18.       
* Individuals using the Internet (% of population) – India (2021): International
Telecommunication Union (ITU) World Telecommunication/ICT Indicators Database. M. Dasgupta (2009): Cyber Crime in India: A Comparative Study, Eastern Law House
Private Ltd., 54, Ganesh Chunder Avenue, Kolkata – 700013.        
* A. Bhangla and J. Tuli (2021): A Study of Cyber Crime and its Legal Framework in
India, International Journal of Law Management and Humanities, Volume 4, Issue 2,
493-504.


